---
title: searches
---


Use to either setup and import searches OR/and to read search metadata from Zotero

```{r setup}

pacman::p_load_gh("kaitlynhair/rwos")
pacman::p_load(openalexR, magrittr, purrr, tidyr, tibble, dplyr, rscopus)

#There's also some scholar and google possibility

```


Map the topic space 

1. epistemic cognition OR epistemological beliefs OR epistemic beliefs OR epistemic thinking OR personal epistemology 
2. socioscientific issues (SSI) teaching and curriculum
3. synthesis writing
4. possibly VUCA (volatility, uncertainty, complexity, ambiguity) 

And their application to:

1. teacher education
2. learning design
3. classroom interaction
4. curriculum
5. "design patterns" OR "toolkit" OR ...
6. "edtech" ?

```{r testqueries}




```



```{r retrievequeries}
data_file <- fs::dir_ls("data/", regexp = "search_output_")
data_date <- stringr::str_extract(data_file, "\\d{4}-\\d{2}-\\d{2}")

if(any(
  length(data_file)>0, #does data exist, and 
  Sys.Date()<=data_date)){

terms <- paste('"epistemic cognition"', '"epistemological beliefs"', '"epistemic beliefs"', sep = "|")
term_core <- '"epistemic cognition"'

epcog_raw <- openalexR::oa_fetch(
entity = 'works',
filter = paste0("from_publication_date:", data_date),
search = term_core) %>%
  mutate(term_core_in_raw = TRUE)

epcog_ft <- openalexR::oa_fetch(
entity = 'works',
filter = paste0("from_publication_date:", data_date),
fulltext.search = terms) %>%
  mutate(terms_in_ft = TRUE)

epcog_ab <- openalexR::oa_fetch(
entity = 'works', 
filter = paste0("from_publication_date:", data_date),
abstract.search = terms) %>%
  mutate(terms_in_ab = TRUE)


epcog_ti <- openalexR::oa_fetch(
entity = 'works', 
filter = paste0("from_publication_date:", data_date),
title.search = terms) %>%
  mutate(terms_in_ti = TRUE)

epcog <- bind_rows(epcog_ab, epcog_ft, epcog_raw, epcog_ti)

last_saved <- Sys.Date()

readr::write_rds(epcog, paste0("data/search_output_", last_saved, ".rds"))

} else {
  
  epcog <- readr::read_rds(data_file)
}

epcog %>% filter(if_any(everything(), ~stringr::str_detect(., "learning"))) %>% nrow()


```


